Evolution of pre-copulatory and post-copulatory inbreeding behaviour and associated

### 2017-03-10 ms_pre_post.Rmd
Minor Introduction tweaks

---
title: Evolution of pre-copulatory and post-copulatory inbreeding behaviour and associated
  polyandry
author: ''
date: "December 15, 2016"
output:
  pdf_document:
    fig_caption: yes
  html_document: default
  word_document:
    fig_caption: yes
    pandoc_args:
    - --csl
    - evolution.csl
    reference_docx: docx_template.docx
header-includes:
- \usepackage{natbib}
- \usepackage{lineno}
- \linenumbers
- \bibliographystyle{amnatnat}
linestretch: 2
csl: evolution.csl
bibliography: ms_pre_post.bib
---

@@

<!--- I don't know of any review articles or meta-analyses that look at polyandry to avoid inbreeding. At least, none within the last 10 years. --->
<!--- I'm not sure I understand the point of ''tractable systems'' for post-copulatory inbreeding avoidance -- why not just 'species', as with pre-copulatory? --->
<!--- What is the difference between 'rationalised' and 'interpreted'? Do these refer to the same thing, and if so, can we get rid of 'rationalised'? --->
<!--- I still think that the end of this paragraph misses the point a bit with regard to how theory is supposed to function. --->

Developing theory on evolution of polyandry given inbreeding depression, @Duthie used a genetically-explicit individual-based model to examine the conditions under which polyandry is predicted to evolve solely due to selection stemming from pre-copulatory inbreeding avoidance. A recent genetically-explicit individual-based model examined the conditions under which polyandry is predicted to evolve solely due to selection stemming from pre-copulatory inbreeding avoidance [@Duthie]. Evolution of polyandry occurred only under highly restricted conditions, requiring that direct negative selection (i.e., 'costs') on polyandry were small, that very few males were available for a female's initial mate choice but many were available for additional mate choice(s), or that polyandry was conditionally expressed when a focal female was related to her initial mate [@Duthie]. Without these conditions, increasing polyandry tended to increase rather than decrease the overall degree of inbreeding that females experienced, and hence reduce offspring fitness. This occurred because, once pre-copulatory inbreeding avoidance evolved, polyandrous females had already chosen available unrelated males as their initial mates. Their additional mates, chosen from the remaining male population, were therefore increasingly likely to include relatives. Evolution of polyandry purely to facilitate pre-copulatory inbreeding avoidance, and hence the resulting degree of inbreeding avoidance, was consequently restricted [@Duthie].

<!--- I don't think 'provide initial theory' is particularly clear (i.e., 'initial' in what respect?), so I've made an edit to the first sentence, though it does seem slightly redundant in both of our cases. --->

@@

Ultimately, the absolute and relative frequencies of alleles underlying pre-copulatory and post-copulatory inbreeding avoidance and polyandry will depend not only on the magnitudes of positive indirect selection stemming from reduced inbreeding depression in females' offspring, but also on the magnitudes of direct negative selection on resulting phenotypes (i.e., the direct fitness costs of expressing each reproductive strategy). Polyandrous females can pay costs of mate searching or mating, for example, because these activities increase predation risk [e.g., @Rowe1988; @Ronkainen1994; @Koga1998]. Females that express pre-copulatory choice and consequent reluctance to mate with relatives might pay costs of increased risk of complete mating failure or harm caused by sexual conflict [@Rowe1994; @Kokko2013]. Females that express post-copulatory choice might pay initial energetic costs associated with developing the physiological or biochemical mechanisms needed to store sperm and successfully bias fertilisation [e.g., @Gasparini2011; @Tuni2013; @Fitzpatrick2014b]. If the relative costs of pre-copulatory and post-copulatory inbreeding avoidance differ, then alleles underlying the less costly strategy might become fixed over generations, while alleles underlying the more costly inbreeding strategy might become extinct if their effects are both costly and made redundant by the less costly strategy. However, such trajectories will also depend on the indirect benefits of each strategy, which might also differ and vary in relation to the evolution of the other strategy. Dynamic models that track the frequencies of alleles underlying multiple reproductive strategies that might influence each other's evolution across generations, and that are enacted among relatives that themselves result from reproductive strategies and inbreeding depression expressed in previous generations, are consequently useful to understand and predict evolutionary outcomes.

@@

<!--- I think that the addition to the last sentence here is probably an improvement, but it still doesn't quite address my question -- there's not much of an argument for concluding that dynamic models are *required*. The implicit argument seems to be something like, ''look, there's a lot of complex stuff that's happening here; we can't figure out how to model how the evolutionary trajectories will play out without a dynamic model, so we're just going to assume that it's not possible''. My tendency is to be careful with these kinds of things, and maybe instead emphasise that dynamic models *can be useful* for understanding these kinds of dynamics without suggesting that they are necessary (time will tell if this is true). --->

>>>>

---
title: Evolution of pre-copulatory and post-copulatory inbreeding behaviour and associated
  polyandry
author: ''
date: "December 15, 2016"
output:
  html_document: default
  pdf_document:
    fig_caption: yes
  word_document:
    fig_caption: yes
    pandoc_args:
    - --csl
    - evolution.csl
    reference_docx: docx_template.docx
header-includes:
- \usepackage{natbib}
- \usepackage{lineno}
- \linenumbers
- \bibliographystyle{amnatnat}
linestretch: 2
csl: evolution.csl
bibliography: ms_pre_post.bib
---

@@

<!--- I don't know of any review articles or meta-analyses that look at polyandry to avoid inbreeding. At least, none within the last 10 years. --->
<!--- I'm not sure I understand the point of ''tractable systems'' for post-copulatory inbreeding avoidance -- why not just 'species', as with pre-copulatory? --->
<!--- ''However, there is yet no theory ...'' seems a bit off; we don't really use the model to predict what combinations should be favoured by selection or weigh in on the above studies... at least, not in a way that is clear to me (if I'm mistaken -- could there be an example of how predictions in one of the above systems follows from our model?). --->
<!--- What is the difference between 'rationalised' and 'interpreted'? Do these refer to the same thing, and if so, can we get rid of 'rationalised'? --->
<!--- I still think that the end of this paragraph misses the point a bit with regard to how theory is supposed to function. --->

Developing theory on evolution of polyandry given inbreeding depression, @Duthie used a genetically-explicit individual-based model to examine the conditions under which polyandry is predicted to evolve solely due to selection stemming from pre-copulatory inbreeding avoidance. Selection for polyandry occurred only under highly restricted conditions, requiring that direct negative selection (i.e., 'costs') on polyandry were small, that very few males were available for a female's initial mate choice but many were available for additional mate choice(s), or that polyandry was conditionally expressed when a focal female was related to her initial mate [@Duthie]. Without these conditions, increasing polyandry tended to increase rather than decrease the overall degree of inbreeding that females experienced, and hence reduce offspring fitness. This occurred because, once pre-copulatory inbreeding avoidance evolved, polyandrous females had already chosen available unrelated males as their initial mates. Their additional mates, chosen from the remaining male population, were therefore increasingly likely to include relatives. Evolution of polyandry purely to facilitate pre-copulatory inbreeding avoidance, and hence the resulting degree of inbreeding avoidance, was consequently restricted [@Duthie].

<!--- Evolution of polyandry often occurred, but it was only under highly restrictive conditions that it was *adaptive* (i.e., evolved due to selection --->
<!--- I don't think 'provide initial theory' is particularly clear (i.e., 'initial' in what respect?), so I've made an edit to the first sentence, though it does seem slightly redundant in both of our cases. --->

@@

Ultimately, the absolute and relative frequencies of alleles underlying pre-copulatory and post-copulatory inbreeding avoidance and polyandry will depend not only on the magnitudes of positive indirect selection stemming from reduced inbreeding depression in females' offspring, but also on the magnitudes of direct negative selection on resulting phenotypes (i.e., the direct fitness costs of expressing each reproductive strategy). Polyandrous females can pay costs of mate searching or mating, for example, because these activities increase predation risk [e.g., @Rowe1988; @Ronkainen1994; @Koga1998]. Females that express pre-copulatory choice and consequent reluctance to mate with relatives might pay costs of increased risk of complete mating failure or harm caused by sexual conflict [@Rowe1994; @Kokko2013]. Females that express post-copulatory choice might pay initial energetic costs associated with developing the physiological or biochemical mechanisms needed to store sperm and successfully bias fertilisation [e.g., @Gasparini2011; @Tuni2013; @Fitzpatrick2014b]. If the relative costs of pre-copulatory and post-copulatory inbreeding avoidance differ, then alleles underlying the less costly strategy might become fixed over generations, while alleles underlying the more costly inbreeding strategy might become extinct if their effects are both costly and made redundant by the less costly strategy. However, such trajectories will also depend on the indirect benefits of each strategy, which might also differ and vary in relation to the evolution of the other strategy. Dynamic models that track the frequencies of alleles underlying multiple reproductive strategies that might influence each others evolution across generations, and that are enacted among relatives that themselves result from reproductive strategies and inbreeding depression expressed in previous generations, are consequently useful to understand and predict evolutionary outcomes.

@@

<!--- I think that the addition to the last sentence here is probably an improvement, but it still doesn't quite address my question -- there's not much of an argument for concluding that dynamic models are *required*. The implicit argument seems to be something like, ''look, there's a lot of complex stuff that's happening here; we can't figure out how to model how the evolutionary trajectories will play out without a dynamic model, so we're just going to assume that it's not possible''. My tendency is to be careful with these kinds of bold claims, and maybe instead emphasise that dynamic models *can be useful* for understanding these kinds of dynamics without suggesting that they are necessary (time will tell if this is true -- I don't want to dissuade someone from giving it a shot -- Corina tarnita, whose work I've often disagreed with, made a good point about this in a recent comment of Physics of Life Reviews). --->
